# 1. Introduction
This is an exercise, a challenge given out by RevoU, an Indonesian online tech academy, to public who follows their YouTube live sessions to practice the main responsibilities of a data analyst.
*****
## 1.1 Case Study Instruction
**Context**
Gaming industry is an interesting field to explore, it would be fun knowing who is the most popular publishers and developers, and which games are the most popular.
*****
## 1.2 Content data

* Name: Name of the game
* Sales: Sales of the game
* Series: Series of the game
* Release: Release of the game
* Genre: Genre of the game
* Developer: Developer of the game
* Publisher: Publisher of the game

*****
## 1.3 Questions to be answered

* Which game is the oldest and the newest games in that dataset?
* Which publisher published most of the games?
* Which developer developed most of the games?
* Which series is the most sales?
* Which series have the most games?

*****
# 2. Preparing the Data
This phase is where I will prepare the data for cleaning and analysis.
*****
## 2.1 Assigning Variables
```{r Assigning Variables}
games_sales <- read.csv("../input/games-sales-revou-challenge-dataset/Games Sales - RevoU Challenge.csv")
```
*****
## 2.2 Install Packages
Prepare the packages for further cleaning, analysis, and visualizations.
```{r}
install.packages("tidyverse")
install.packages("lubridate")
```
*****
## 2.3 Load the Packages
```{r Package Load}
library(tidyverse)
library(lubridate)
```
*****
## 2.4 Preview Dataset
I'll be using the head() and summary() to preview the details of the data.
```{r Head function}
head(games_sales)
```

```{r Summary function}
summary(games_sales)
```

```{r Colnames function}
colnames(games_sales)
```

*****
# 3. Data Cleaning
As seen in glimpse, all data except the Sales field are characters.
```{r Glimpse function}
glimpse(games_sales)
```

Now we need to check for any duplications.
```{r Sum duplicated}
sum(duplicated(games_sales))

games_sales <- distinct(games_sales)
```
2 rows are duplicated, and they are removed.

Since all the data are mandatory to answer the questions, even with many NA values in the Series field, I will keep the column in the analysis and visualization phase.

##3.1 Data Formatting
```{r formatted_table}
# Create a new table: formatted_table
formatted_table <- games_sales %>%
  rename(date = Release) %>%
  mutate(date = as_date(date, format = "%m/%d/%Y"))
```


*****
# 4. Data Analysis & Visualization

```{r}
# Bar chart for Steps

```

*****
# 5. Answering stakeholder's Questions
This part is where I'll be answering the questions. 

## 5.1 Which game is the oldest and the newest games in that dataset?
```{r Sorting table}
# Date sorted from oldest
oldest_date <- formatted_table[order(as.Date(formatted_table$date)),]

head(oldest_date)

# Date sorted from earliest
earliest_date <- formatted_table[rev(order(as.Date(formatted_table$date))),]

head(earliest_date)
```
**Answer:**
* Oldest game: Hydlide
* Newest game: Valheim

## 5.2 Which publisher published most of the games?
```{r Most published by Publisher}
most_published <- formatted_table %>%
  group_by(Publisher) %>%
  summarise(total_published = n()) %>%
  arrange(desc(total_published))

head(most_published)
```
**Electronic Arts** is the publisher that published most of the games.

## 5.3 Which developer developed most of the games?
```{r Most Developed by Developer}
# New table for Most Developed
most_developed <- formatted_table %>%
  group_by(Developer) %>%
  summarise(total_developer = n()) %>%
  arrange(desc(total_developer))

# View table
head(most_developed)
```
**Blizzard Entertainment** is the developer that developed most of the games.

## 5.4 Which series is the most sales?
```{r Most Sales by Series}
# New table for Most Sales
series_sales <- formatted_table %>%
  group_by(Series) %>%
  summarise(Sales) %>%
  arrange(desc(Sales))

# Remove rows with NA values
series_sales <- series_sales[!(is.na(series_sales$Series) | series_sales$Series == ""), ]

# View table
head(series_sales)
```
**Minecraft** is the series with most sales.

## 5.5 Which series have the most games?
```{r Series with Most Games}
# New table, total games in Series
series_games <- formatted_table %>%
  group_by(Series) %>%
  summarise(total_games = n()) %>%
  arrange(desc(total_games))

# Remove rows with NA values
series_games <- series_games[!(is.na(series_games$Series) | series_games$Series == ""), ]

# View table
```
**StarCraft** is the series that have the most games.

*****
# 6. Conclusion

* **Which game is the oldest and the newest games in that dataset?**
  * Oldest game: Hydlide, date 1984-12-01
  * Newest game: Valheim, date 2021-02-01
  
* **Which publisher published most of the games?**
  * Electronic Arts

* **Which developer developed most of the games?**
  * Blizzard Entertainment

* **Which series is the most sales?**
  * Minecraft

* **Which series have the most games?**
  * StarCraft